Online Laterality Battery Pre-Processing - short version

### 2020-02-03 battery-preprocessing_v3_DB.Rmd
pointless change to demonstrate commit

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# libraries 
library(readr)
library(yarrr)
library(dplyr)
library(tidyr)
library(car)
library(ggplot2)
library(knitr)
require(readr)  # for read_csv()
require(dplyr)  # for mutate()
require(tidyr)  # for unnest()
require(purrr)  # for map(), reduce()
library(GGally)
require(stringr) # string matching
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# libraries 
library(readr)
library(yarrr)
library(dplyr)
library(tidyr)
library(car)
library(ggplot2)
library(knitr)
require(readr)  # for read_csv()
require(dplyr)  # for mutate()
require(tidyr)  # for unnest()
require(purrr)  # for map(), reduce()
library(GGally)
require(stringr) # string matching
library(maps)
```
